Quantitative review of the effects of triazole and benzimidazole fungicides on Fusarium head blight and wheat yield in Brazil

### 2017-07-28 article.Rmd
teste
Formatting issues

Since the log of the response ratios equal the difference of logs, the differences between pairs of the elements in µ, as well as their standard errors and 95% confidence intervals were obtained (Paul et al. 2008). Thus, the overall mean log of the response ratio (L̅) for each fungicide treatment relative to the non-treated check was estimated as L ̅" = " "μ"  ̂_"Treat "  "- " "μ"  ̂_"Check" , where "μ"  ̂_"Treat"   and "μ"  ̂_"Check"  are estimated mean log FHB index or yield for a treatment (Treat) and the non-treated check (Check), respectively. Overall mean percent FHB control and mean yield increase and their confidence intervals were obtained by back-transforming "L"  ̅_IND and "L"  ̅_YLD and the upper and lower limits of the confidence intervals around "L"  ̅_"IND"  and "L"  ̅_"YLD"  as "C"  ̅ = (1-(exp("L"  ̅_"IND"  ))×100) and Y ̅ = ((exp("L"  ̅_"YLD" )-1)×100), respectively. The mean difference in yield (D̅) was estimated directly by the difference between the estimates for the fungicide treatment and the non-treated check (Madden et al., 2016).

>>>>

Since the log of the response ratios equal the difference of logs, the differences between pairs of the elements in µ, as well as their standard errors and 95% confidence intervals were obtained (Paul et al. 2008). Thus, the overall mean log of the response ratio (*L*) for each fungicide treatment relative to the non-treated check was estimated as L ̅" = " "μ"  ̂_"Treat "  "- " "μ"  ̂_"Check" , where "μ"  ̂_"Treat"   and "μ"  ̂_"Check"  are estimated mean log FHB index or yield for a treatment (Treat) and the non-treated check (Check), respectively. Overall mean percent FHB control and mean yield increase and their confidence intervals were obtained by back-transforming "L"  ̅_IND and "L"  ̅_YLD and the upper and lower limits of the confidence intervals around "L"  ̅_"IND"  and "L"  ̅_"YLD"  as "C"  ̅ = (1-(exp("L"  ̅_"IND"  ))×100) and Y ̅ = ((exp("L"  ̅_"YLD" )-1)×100), respectively. The mean difference in yield (D̅) was estimated directly by the difference between the estimates for the fungicide treatment and the non-treated check (Madden et al., 2016).
